### 2017-03-01 paper/chapters/conclusion.tex
restructured conclusion/summary

In this article we have taken a look at different directed models which perform generative modeling using deep neural networks.
Variational autoencoders as well as generative adversarial networks have shown to produce good results using large datasets with unsupervised learning.
Deep generative models have shown to learn rich internal representation of high-dimensional data in order to generate samples.
Going further, as intelligent agents will need to have accurate and generalized internal representations inferred through sensory input to reason about the world, generative models are are likely to be the cornerstones of more advanced intelligent systems in the future.

Both models explained in detail have been proposed in recent years with many proposed extensions which were not covered in this article, thus further improvements are likely to happen.

>>>>

In this article we have taken a look at different directed models which perform generative modeling using deep neural networks.\\
After a short overview over traditional generative models and models not covered in this article, we have taken a look at a wide area of applications using generative models.\\\\
%
As one of the first basic generative models, the sigmoid belief net lays the foundation for directed generative models and displays its weaknesses during inference and training.\\
The variational autoencoders have been discussed in more detail using variational inference to turn the inference problem into an optimization problem and solving it there.
VAE and its various extensions have been shown to be a flexible tool applicable for different tasks.\\
%
Generative adversarial networks introduced in Section~\ref{sec:gan} uses a game-theoretic approach to generative modeling. In recent years, GANs have been extended of which we discussed a subset.\\\\
%
Deep generative models have shown the capability to learn rich internal representation of high-dimensional data in order to generate samples using recent advances in deep learning.
Going further, as intelligent agents will need to have accurate and generalized internal representations inferred through sensory input to reason about the world, generative models are likely to be the cornerstones of more advanced intelligent systems in the future.

%Both models explained in detail have been proposed in recent years with many proposed extensions which were not covered in this article, thus further improvements are likely to happen.
